---
title: "Tutorial"
author: "Michael Rustler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 1 Install R package

```{r, eval = FALSE}
installed_packages <- rownames(installed.packages())

if(!"devtools" %in% installed_packages) {
  install.packages("devtools", repos = "https://cloud.r-project.org")
}
if(!"kwb.pkgstatus" %in% installed_packages) {
  devtools::install_github("KWB-R/kwb.pkgstatus")
}

```

# 2 How to check KWB R package status 

## 2.1 Parameterise

Define path to `secrets.csv` and define repositories for the Github organisation
`KWB-R` which are not R packages and save them in a variable called 
`non_r_packages`. Then call the 

```{r}
secrets_csv <- "secrets.csv"

non_r_packages = c("kwb-r.github.io",
  "fakin.blog", "fakin.doc", "HydroServerLite")

```

## 2.2 Get dataframe of R package status information

Run the function `kwb.pkgstatus::prepare_status_rpackages` with parameters 
defined above:

```{r eval = FALSE}
pkgstatus_df <- kwb.pkgstatus::prepare_status_rpackages(secrets_csv, 
                                                        non_r_packages)

head(pkgstatus_df)
```

## 2.3 Create R package status report

Run the function `kwb.pkgstatus::create_report_rpackages` with parameters 
defined above:


```{r eval = FALSE}

temp_dir <- temp()

cat(sprintf("Save report in temp folder:\n", temp_dir))
kwb.pkgstatus::create_report_rpackages(secrets_csv, 
                                       non_r_packages, 
                                       export_dir = temp_dir)
)

```

